Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-07-12 Paper/paper.tex
Update text

\subsection{Photon underproduction at $z=0$?}
% Kollmeier number of ~10 times higher than HM12 in figure.

%% JFH I disagree with your approach here. It is not interesting to simply extrapolate your z > 0.6 to these
%% redshifts in my opinion, when you have the ability to fit them or at least to show the binned fits if you cannot
%% get a global model to work. Why is it interesting to write an entire section on an extrapolation?

\textbf{Comments from GW:\\
1. State again that we need to use the emissivity fit due to the redshift effects. Extrapolated emissivity agrees well with our direct estimates (open symbols in emissivity plot) and with other LFs (Schulze)\\
2. Section needs revision to account for SED change in Fig. 10.\\
3. We need to be clear whether we are plotting Gamma as is, or whether we are recalculating using your code but other peoples' emissivities.\\
4. We are comparable to HM12, but HM12 considers all AGN. We are higher if we consider fainter AGN. Given that we miss a factor of 2 to get the forest measurements, we should give a number how faint we need to go.\\
5. Gamma depends on $f(N,z)$. Shull doesn't match the measured $f(N,z)$, but Gaikwad and Kollmeier do. Gaikwad also estimates the uncertainty in Gamma from the assumed $f(N,z)$. To claim any PUC, one has to run UVB synthesis models with a realistic $f(N,z)$ accounting large uncertainty in the range for LLSs (this is hard at low z due to the low number density and need for space-based surveys). Shull et al. 2017 present results from a survey of low-z partial LLSs (their Fig. 11). If the HM12 $f(N,z)$ is inconsistent with the measurements, Gamma won't be right even if the emissivity is right. Only Gaikwad investigates this a bit.\\
6. Discuss deficit of Gamma:  Factor ~2 deficit for -18. Explanations: 1. Changes in limiting magnitude, and spectral index (put numbers: Scott index for -23 no deficit for -18 limit, Scott index for all QSOs: no deficit for -21, fainter AGN: insignificant increase at limit -14 covered by Schulze due to shallow faint-end slope). 2. Galaxies? Cite low-z leakers (Izotov), but rare objects. 
}

@@

Figure~\ref{fig:puc} shows the evolution of the \HI\ photoionization
rate due to AGN in our model for luminosity function integration
limits of $M_{1450}=-21$ and $-18$ at redshifts $z<3$.  Note that this
photoionization rate is derived by fitting the model from
Equation~(\ref{eqn:e912fit}) to the emissivities obtained from
luminosity functions in various redshift bins.  While doing this, as
discussed above, redshift bins that were interpreted as being affected
by systematic errors were ignored.  As a result, the emissivity model
used in calculating the photoionization rate is an extrapolation at
$z<0.6$.  However, it is interesting to note that even if we disregard
the $z<0.6$ data due to systematic errors, the extrapolated
emissivities at these redshifts are consistent with the emissivities
calculated from our luminosity function fits to these data for either
of our chosen integration limits.  This can be seen in
Figure~\ref{fig:e912_2}.  We find that the low-redshift
\HI\ photoionization rate in our model is higher than that in the
\citet{2012ApJ...746..125H} UVB model by a factor of 1.2 for
$M_{1450}<-21$ and a factor of 2 for $M_{1450}<-18$.  The
photoionization rate obtained when the faint AGN ($M_{1450}<-18$) are
included is consistent with a variety of recent estimates.  This rate
is in reasonable agreement with the photoionization rate found by
\citet{2017MNRAS.467.3172G}, who found that this photoionisation rate
is sufficient to explain the \HI\ column density distribution measured
by \citet{2016ApJ...817..111D}, thus alleviating the photon
underproduction problem without requiring additional contribution of
hydrogen-ionizing photons from galaxies.  At $z<0.5$, this
photoionization rate evolution in our model appears consistent also
with that derived by \citet{2015MNRAS.451L..30K} using the quasar
luminosity function measurements of \citet{2009MNRAS.392...19C} and
\citet{2013A&A...551A..29P}, although the evolution is somewhat
shallower in our model at $z>0.5$.  The model of
\citet{2015ApJ...813L...8M} also agrees with our $M_{1450}<-18$
inference at $z<0.7$.  \citet{2015ApJ...811....3S} compared the
\HI\ column density distribution measurements to cosmological
simulations with an enhanced photoionization rate relative to the
\citet{2012ApJ...746..125H} model to find that
$\Gamma_\mathrm{HI}=4.6\times 10^{-14}(1+z)^{4.4}\,\mathrm{s}^{-1}$
produces the observed \HI\ column densities.  This photoionization
rate was achieved in the simulations of \citet{2015ApJ...811....3S} by
a combination of quasars and galaxies (with an escape fraction of
hydrogen-ionizing photons assumed to be $f_\mathrm{esc}=0.05$).  As
seen in Figure~\ref{fig:puc}, this photoionization rate agrees with
our model at $z\sim 0$ for $M_{1450}<-18$, although it evolves
somewhat more rapidly at higher redshifts.  The photoionization rate
estimate by \citet{2017MNRAS.467.4802F} from the H$\alpha$ surface
brightness of a $z\sim 0$ galaxy observed by VLT/MUSE is somewhat
higher than even our $M_{1450}<-18$ determination.  However, it is
possible that the \citet{2017MNRAS.467.4802F} estimate is an upper
limit, as the contribution of local sources to the photoionization
rate is neglected in their modelling.  The requirement of an enhanced
photoionization rate at $z\sim 0$ relative to
\citet{2012ApJ...746..125H} UVB model is also confirmed by the
simulations presented by \citet{2017MNRAS.467L..86V},
\citet{2017ApJ...837..106O}, and \citet{2018arXiv180104931P}.  But
note that, as discussed above in Section~\ref{sec:e912}, a direct
comparison of our results with the models of
\citet{2015ApJ...813L...8M}, \citet{2015MNRAS.451L..30K}, and
\citet{2018arXiv180104931P} is difficult because of the inhomogenous
redshift-dependent integration limits adopted by these authors.

@@

We now consider the implications of our AGN luminosity function models
for \ion{He}{ii} reionization. The time evolution of the
volume-averaged \ion{He}{iii} fraction $Q_\ion{He}{iii}$ is given by
\citep[e.g.][]{2012ApJ...746..125H}
\begin{equation}
  \frac{\mathrm{d}Q_\ion{He}{iii}}{\mathrm{d}t}=\frac{\dot{n}_\mathrm{ion,4}}{\langle n_\mathrm{He}\rangle}-\frac{Q_\ion{He}{iii}}{\langle t_\mathrm{rec,He}\rangle}\quad,
  \label{eqn:qHedot}
\end{equation}
where $\dot n_\mathrm{ion,4}$ is the emission rate of $\ge 4$\,Ry photons per unit proper volume,
$\langle n_\mathrm{He}\rangle$ is the average proper helium number density,
and $\langle t_\mathrm{rec,He}\rangle$ is the average recombination time scale for \ion{He}{iii}.
%% GW simplified the following. All of that is a simple rescaling of the 912A emissivity
%We obtain the evolution of $\dot n_{\rm ion,4}$ for AGN with $M_\mathrm{1450}<-21$ and
%$M_\mathrm{1450}<-18$ by integrating the contribution of double power
%law luminosity function obtained in distinct redshifts bins and
%fitting Equation~(\ref{eqn:e912fit}) to the resultant \HeII-ionizing emissivities.
%We extrapolate the resultant fit to $z>7$, although the
%contribution from this extrapolated emissivity to \HeII-reionization is small.
With our quasar emissivity model from Section~\ref{sec:e912} the emission rate
can be written as
%\begin{eqnarray}\nonumber
%\dot n_\mathrm{ion,4}\left(z\right)&=&\left(1+z\right)^3\int_{\nu_{228}}^{\infty}\mathrm{d}%\nu\frac{\epsilon_\nu\left(\nu,z\right)}{h\nu}\\
%&=&-\frac{4^{\alpha_\nu}}{h\alpha_\nu}\left(1+z\right)^3\epsilon_{912}\left(z\right)\quad,
%\end{eqnarray}
\begin{equation}
\dot n_\mathrm{ion,4}\left(z\right)=-\frac{4^{\alpha_\nu}}{h\alpha_\nu}\left(1+z\right)^3\epsilon_{912}\left(z\right)\quad,
\end{equation}
with the quasar spectral index $\alpha_\nu=-1.7$ and the comoving 912\,\AA\ emissivity
$\epsilon_{912}\left(z\right)$ given by Equations~\eqref{eqn:e912_18} and \eqref{eqn:e912_21}
for $M_{1450}<-18$ and $M_{1450}<-21$, respectively.
The recombination time scale in Equation~\eqref{eqn:qHedot} is given by
\begin{equation}
  \langle t_{\rm rec}\rangle=[(1+2\chi) \langle n_\mathrm{H}\rangle \alpha_\mathrm{B}\,C]^{-1}\quad,
  \label{eq:trec}
\end{equation}
where $\langle n_\mathrm{H}\rangle=1.881\times
10^{-7}(1+z)^3$~cm$^{-3}$ is the average proper hydrogen number density,
$\alpha_\mathrm{B}$ is the Case~B \ion{He}{iii} recombination coefficient \citep{1997MNRAS.292...27H},
and $\chi=0.079$ is the cosmic number fraction of helium for a cosmic
helium mass fraction of $Y_\mathrm{He}=0.24$. 
We assume that the clumping factor $C$ for helium is the same as for hydrogen,
for which \citet{2012ApJ...747..100S} obtained
\begin{equation}
  C = 2.9\left(\frac{1+z}{6}\right)^{-1.1}
\end{equation}
over the redshift range $5<z<9$.

@@

%% JFH I think these next two paragraphs here needs to be shortened considerably.
%% You are spending way to to much time and text discussing the literature. 
%% GW commented the previous version and provided a shorter one

Figure~\ref{fig:qhe} also shows previous solutions of Equation~\eqref{eqn:qHedot}
with different parameterizations of the quasar emissivity, spectral energy distribution and
clumping factor \citep{2012ApJ...746..125H,2015ApJ...813L...8M,2016ApJ...828...90L,2018arXiv180104931P},
as well as the results from cosmological radiative transfer simulations of \ion{He}{ii} reionization \citep{2009ApJ...694..842M,2014MNRAS.445.4186C}.
The differences of our results to the ones by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
mostly result from differences in the adopted quasar emissivity (Figure~\ref{fig:e912_2}).
The large quasar emissivity adopted by \citet{2015ApJ...813L...8M} results in an early completion of
\ion{He}{ii} reionization at $z\approx 4$, which is inconsistent with the measured strong \ion{He}{ii} absorption
at $2.7<z<3$ \citep{2016ApJ...825..144W,2018MNRAS.473.1416M,2018arXiv180104931P}
if the \ion{He}{ii}-ionizing background is not fluctuating on large scales due to rare clustered and/or short-lived
quasars that result in a spatially varying mean free path of \ion{He}{ii}-ionizing photons
\citep{2010ApJ...714..355F,2014MNRAS.440.2406M,2014MNRAS.437.1141D,2017MNRAS.465.2886D}.
The quasar emissivity considered by \citet{2012ApJ...746..125H} falls below our determinations at the relevant
redshifts (Figure~\ref{fig:e912_2}), which results in a delayed completion of \ion{He}{ii} reionization at $z\simeq 2.8$.

@@

In Figure~\ref{fig:qhe} we also plot $Q_\ion{He}{iii}\left(z\right)$ from two numerical simulations of quasar-driven
\ion{He}{ii} reionization \citep{2009ApJ...694..842M,2014MNRAS.445.4186C} that broadly reproduce the measured
\ion{He}{ii} effective optical depths \citep{2016ApJ...825..144W}. In these simulations the outputs of $N$-body or
hydrodynamic simulations are post-processed with radiative transfer around quasars sourced according to a specific model,
and the effects of \ion{He}{ii} Lyman limit systems are approximately captured with sub-grid filtering methods
\citep{2009ApJ...694..842M} or with adaptive mesh refinement \citep{2014MNRAS.445.4186C}.
Their different timing of \ion{He}{ii} reionization is mostly due to the adopted quasar model
(QLF, spectral energy distribution, quasar lifetime, anisotropic emission, halo mass range) and stochasticity in the
$z\ga 3.5$ quasar number density in the limited simulation volumes.
Thus, while current simulations do not reproduce the measured scatter in the \ion{He}{ii} effective optical depths at
$2.7<z<3.5$ in detail \citep{2016ApJ...825..144W}, this may reflect limitations of the modelling other than the QLF
\citep{2017MNRAS.468.4691D}. Our $Q_\ion{He}{iii}\left(z\right)$ for $M_{1450}<-18$ agrees well with the simulation
by \citet{2014MNRAS.445.4186C}, in which \ion{He}{ii} reionization is accomplished by the $z<5$ quasar population
evolved assuming pure density or pure luminosity evolution to match the QLF by \citet{2011ApJ...728L..26G} for
$M_{1450}<-19.5$ \citep[see also][]{2013MNRAS.435.3169C}. Future efforts in numerical modelling of \ion{He}{ii}
reionization should investigate quasar models which follow the QLF evolution in detail, and which are consistent with
the measured redshift evolution and scatter of the \ion{He}{ii} effective optical depth, as well as the measured redshift evolution
of the IGM temperature-density relation \citep[e.g.][]{2011MNRAS.410.1096B,2014MNRAS.441.1916B,2018MNRAS.474.2871R,2017arXiv171000700H}.

%% Previous version commented by GW
%In Figure~\ref{fig:qhe}, we also show the reionization histories from
%other models of \HeII\ reionization in the literature.  Our model
%curve for $M_\mathrm{1450}<-21$ is closest in agreement to the
%simulations of \citet{2009ApJ...694..842M} and the analytical model of
%\citet{2018arXiv180104931P}.  \citet{2018arXiv180104931P} model the
%\HeII-ionizing emissivity of AGN by fitting the functional form in
%Equation~(\ref{eqn:e912fit}) to the emissivities reported by
%\citet{2009A&A...507..781S}, \citet{2007A&A...472..443B}, and
%\citet{2012ApJ...755..169M}.  The resultant emissivity in the model of
%\citet{2018arXiv180104931P} is similar in shape but higher in
%amplitude than the emissivity in the \citet{2012ApJ...746..125H}
%model.  The \HeII-ionizing emissivity of \citet{2018arXiv180104931P}
%is closer to our inference for $M_\mathrm{1450}<-21$ than the model of
%\citet{2012ApJ...746..125H}.  (However, note that both these models
%suffer from inhomogeneous luminosity function integration limits, as
%the integration limit is set to a fixed fraction of the break
%luminosity, as discussed above in Section~\ref{sec:e912}.)  A spectral
%index of $\alpha_\mathrm{EUV}=-1.7$ is assumed.
%\citet{2018arXiv180104931P} compute the evolution of $Q_\nHeIII$ by
%evolving the \HeIII\ ionization fraction in a gas cloud with the mean
%cosmic baryonic density exposed to the average \HeII-ionizing flux.
%The ionizing flux is obtained by filtering the ionizing emissivity
%through an inhomogeneous IGM in which the column density distribution
%of \HeIII\ is derived from that of \HI\ in a manner similar to
%\citet{2012ApJ...746..125H}.  As a result, this model incorporates the
%effect of \HeII\ Lyman-limit systems, and the $Q_\nHeIII$ evolution in
%this model deviates from our predictions towards the end of
%reionization, as seen in Figure~\ref{fig:qhe}.  Comparing the
%emissivity model in the cosmological radiative transfer simulations of
%\citet{2009ApJ...694..842M} with our models is less straightforward.
%Quasars are modelled in the simulations of \citet{2009ApJ...694..842M}
%by relating quasar luminosities and lifetimes to halo masses following
%the galaxy-merger-induced quasar activity model of
%\citet{2005ApJ...630..705H}.  The resultant bolometric quasar
%luminosity functions are somewhat shallower than those of
%\citet{2007ApJ...654..731H}, but with a higher amplitude.  A spectral
%index of $\alpha_\mathrm{EUV}=-1.6$ is assumed.  Figure~\ref{fig:qhe}
%shows that the resultant reionization history in these simulations
%agrees with our model for $M_\mathrm{1450}<-21$, except towards the
%end of reionization, where, as before, \HeII\ Lyman-limit systems
%become important.

%Helium reionization is delayed in the model of
%\citet{2012ApJ...746..125H} due to their reduced emissivity at $z\sim
%3$.  In the \citet{2015ApJ...813L...8M} model, a significant
%\HeII\ fraction is ionized already at $z=6$, and reionization is
%complete by $z=4.1$ due to the very high emissivity assumed in this
%model.  In the radiation-hydrodynamic simulations by
%\citet{2016ApJ...828...90L}, the AGN population is calibrated to the
%SDSS \citep{2013ApJ...768..105M} and COSMOS
%\citep{2012ApJ...755..169M} data at $z>3.5$, combined with a model for
%quasar light curves.  The fiducial \HeII\ reionization history
%obtained by these authors is shown in Figure~\ref{fig:qhe} along with
%an estimate of the uncertainty.  Reionization ends considerably later
%in this model ($z\sim 2.6$).  The \HeII\ reionization history in our
%model for $M_\mathrm{1450}<-18$ agrees closely with that in the
%radiative transfer simulations presented by
%\citet{2014MNRAS.445.4186C}.  The AGN population in these simulations
%is `turned on' at $z=5$ and evolved assuming a pure luminosity
%evolution to match the inferred luminosity function of
%\citet{2011ApJ...728L..26G}.  The somewhat early reionization in the
%simulations of \citet{2014MNRAS.445.4186C} relative to most other
%models shown in Figure~\ref{fig:qhe} may be driven by the
%significantly higher emissivity from AGN with intermediate brightness
%($M_{1450}\sim -23$) in the model of \citet{2011ApJ...728L..26G}.
%However, the limited numerical resolution of these simulations may
%also play a role \citep{2014MNRAS.445.4186C}.

%An important constraint on \HeII\ reionization can be derived from the
%thermal history of the IGM.  \citet{2018MNRAS.473.1416M} constrained
%the evolution of the 912\,\AA\ emissivity of AGN by assuming a
%spectral index of $\alpha_\mathrm{EUV}=-1.57$ and using the
%measurements of the effective \HeII\ \lya optical depth
%\citep{2016ApJ...825..144W} and the IGM temperature
%\citep{2011MNRAS.410.1096B}.  \citet{2018MNRAS.473.1416M} found that
%although these data favour a reionization history in which \HeII\ is
%reionized at $z>4$, the 912\,\AA\ emissivity of AGN is nevertheless
%required to drop rapidly at $z>3$.  This emissivity evolution is much
%more rapid than that in our model for $M_\mathrm{1450}<-21$, with the
%caveat that the constraint derived by \citet{2018MNRAS.473.1416M} is
%model-dependent and assumes a shallower EUV spectrum.  A steeper
%spectrum with $\alpha_\mathrm{EUV}=-1.8$ was assumed in a recent model
%by \citet{2018arXiv180109693K}.  The resultant emissivity evolution is
%consistent with our model for $M_\mathrm{1450}<-21$, although somewhat
%more rapid at $z>2$.  The AGN luminosity function is derived by
%combining determinations from various data sets
%\citep{2015MNRAS.451L..30K}.  An inhomogeneous integration limit of
%$0.01L_*$ is applied to calculate the emissivity.  \HeII\ reionization
%ends at $z=2.8$ in the model of \citet{2018arXiv180109693K}.
%(\citealt{2017MNRAS.471..255K} argued that for their luminosity
%function model, spectra with $\alpha_\mathrm{EUV}>-1.6$ are unlikely
%to be consistent with the \HeII\ \lya data.)
%\citet{2017MNRAS.468.4691D} considered the effect of an AGN-dominated
%reionization on the \HI\ Ly$\alpha$ opacity at $z>5$,
%\HeII\ Ly$\alpha$ opacity at $z\sim 3.1$--$3.3$, and the thermal
%history of the IGM.  These authors found that that any scenario in
%which reionization of \HeII\ completes at $z>3$ is inconsistent with
%the measurements of the IGM temperature at $z=4$--$5$.  We leave the
%analysis of the IGM thermal history implied by our AGN luminosity
%models for future work.

>>>>

\subsection{Photon underproduction at $z=0$?}

@@

Figure~\ref{fig:puc} shows the evolution of the \HI\ photoionization
rate due to AGN in our model for luminosity function integration
limits of $M_{1450}=-21$ and $-18$ at redshifts $z<3$.  Note that we
use the 912\,\AA\ emissivity from Equation~(\ref{eqn:e912_18}) and
(\ref{eqn:e912_21}), which are derived by fitting the model from
Equation~(\ref{eqn:e912fit}) to the emissivities obtained from
luminosity functions in various redshift bins.  While doing this, as
discussed above, redshift bins that were interpreted as being affected
by systematic errors were ignored.  As a result, the emissivity model
used in calculating the photoionization rate is an extrapolation at
$z<0.6$.  However, it is interesting to note that the extrapolated
emissivities at these redshifts are consistent with the emissivities
calculated from our luminosity function fits to the $z<0.6$ data for
either of our chosen integration limits.  This can be seen in
Figure~\ref{fig:e912_2}.  At $z\sim 0$, the comoving
912\,\AA\ emissivity in our model is lower by almost a factor of 2
than that derived from the luminosity function inferred at this
redshift by \citet{2009A&A...507..781S} for the $M_{1450}<-18$ case.
For the $M_{1450}<-21$ integration, our comoving emissivity is higher
than the emissivity in the model of \citet{2009A&A...507..781S} by
about 50\%.  This results from the very faint $M_*$ ($\sim -19$) and
steep faint-end slope ($\beta=-2$) obtained by
\citet{2009A&A...507..781S}.  (See Appendix~\ref{sec:qlfliterature}.)
We use a spectral slope of $\alpha=-1.7$ for
$\lambda<912$\,\AA\ (Equation~\ref{eqn:sed}).

We find that the low-redshift \HI\ photoionization rate in our model
is approximately equal to that that in the \citet{2012ApJ...746..125H}
UVB model for both of our integration limits, as shown in
Figure~\ref{fig:puc}.  At $z\sim 0$, the photoionisation rate for our
$M_{1450}<-21$ integration is lower than \citet{2012ApJ...746..125H}
photoionisation rate by about 10\%.  For the $M_{1450}<-18$ case, the
photoionisation rate is higher than that in the
\citet{2012ApJ...746..125H} model by about 10\%.  These differences
are small compared to the factor of 2 to 3 differences that we find
between our model and several recent estimates.  At $z=0.1$, this rate
is smaller by a factor of 2 than the photoionization rate derived by
\citet{2017MNRAS.467.3172G} from the \HI\ column density distribution
measurements of \citet{2016ApJ...817..111D}.  At $z<0.5$, this
photoionization rate evolution in our model appears lower than also
the rate derived by \citet{2015MNRAS.451L..30K} using the quasar
luminosity function measurements of \citet{2009MNRAS.392...19C} and
\citet{2013A&A...551A..29P}.  The model of \citet{2015ApJ...813L...8M}
also results in a higher ionisation rate than our $M_{1450}<-18$
inference at $z<0.7$.  \citet{2015ApJ...811....3S} compared the
\HI\ column density distribution measurements to cosmological
simulations with an enhanced photoionization rate relative to the
\citet{2012ApJ...746..125H} model to find that
$\Gamma_\mathrm{HI}=4.6\times 10^{-14}(1+z)^{4.4}\,\mathrm{s}^{-1}$
produces the observed \HI\ column densities.  This photoionization
rate was achieved in the simulations of \citet{2015ApJ...811....3S} by
a combination of quasars and galaxies (with an escape fraction of
hydrogen-ionizing photons assumed to be $f_\mathrm{esc}=0.05$).  As
seen in Figure~\ref{fig:puc}, this photoionization rate is in closer
agreement with the \citet{2015ApJ...813L...8M} model.  The
photoionization rate estimate by \citet{2017MNRAS.467.4802F} from the
H$\alpha$ surface brightness of a $z\sim 0$ galaxy observed by
VLT/MUSE is somewhat higher than most other models shown in
Figure~\ref{fig:puc}.  However, it is possible that the
\citet{2017MNRAS.467.4802F} estimate is an upper limit, as the
contribution of local sources to the photoionization rate is neglected
in their modelling.  The requirement of an enhanced photoionization
rate at $z\sim 0$ relative to our inference is also confirmed by the
simulations presented by \citet{2017MNRAS.467L..86V},
\citet{2017ApJ...837..106O}, and \citet{2018arXiv180104931P}.  But
note that, as discussed above in Section~\ref{sec:e912}, a direct
comparison of our results with the models of
\citet{2015ApJ...813L...8M}, \citet{2015MNRAS.451L..30K}, and
\citet{2018arXiv180104931P} is difficult because of the inhomogenous
redshift-dependent integration limits adopted by these authors.

Before considering the deficit in the photoionisation rate obtained
from AGN at low redshifts relative to measurements from the
\lya\ forest as a photon underproduction crisis, it is worthwhile to
recall various assumptions entering our derivation.  With a spectral
index of $-1.7$, our ionisation rate estimate falls short of the
\lya\ forest measurements by a factor of $\sim 2$ with an integration
limit of $M_{1450}=-18$ on the luminosity function.
\citet{2015ApJ...813L...8M} implicitly assume an integration limit of
$M_{1450}=-14$ at $z\sim 0$ (see also \citealt{2015MNRAS.451L..30K,
  2018arXiv180104931P}) as this limit corresponds to $M_*+5$ for the
\citet{2009A&A...507..781S} luminosity function measurement.  It is
unclear if the assumption of unit LyC escape fraction is valid for
such faint AGN, but we find that even with this extremely faint
integration limit, the photoionisation rate deficit is reduced by only
about 25\% for a spectral index of $-1.7$.  While this result does not
change significantly if we assume a spectral index of $-1.4$ as
suggested by \citet{2014ApJ...794...75S}, assuming a much harder
spectrum with a spectral index of $-0.56$ \citep{2004ApJ...615..135S}
for faint ($M_{1450}>-23$) AGN completely alleviates the deficit for
an integration limit of $M_{1450}=-18$.  One should also note that our
ionization rate model ignores the large uncertainties in the
\HI\ column density distribution at the Lyman limit
\citep{2011ApJ...736...42R, 2017ApJ...849..106S, 2017MNRAS.466..838G}.  Alternatively, it
may be possible to balance the ionization rate deficit by the
contribution from low-redshift LyC-leaking galaxies
\citep{2016Natur.529..178I, 2018MNRAS.474.4514I, 2018MNRAS.478.4851I}

@@

We now consider the implications of our AGN luminosity function models
for \ion{He}{ii} reionization. The time evolution of the
volume-averaged \ion{He}{iii} fraction $Q_\ion{He}{iii}$ is given by
\citep[e.g.][]{2012ApJ...746..125H}
\begin{equation}
  \frac{\mathrm{d}Q_\ion{He}{iii}}{\mathrm{d}t}=\frac{\dot{n}_\mathrm{ion,4}}{\langle n_\mathrm{He}\rangle}-\frac{Q_\ion{He}{iii}}{\langle t_\mathrm{rec,He}\rangle}\quad,
  \label{eqn:qHedot}
\end{equation}
where $\dot n_\mathrm{ion,4}$ is the emission rate of $\ge 4$\,Ry
photons per unit proper volume, $\langle n_\mathrm{He}\rangle$ is the
average proper helium number density, and $\langle
t_\mathrm{rec,He}\rangle$ is the average recombination time scale for
\ion{He}{iii}.  With our quasar emissivity model from
Section~\ref{sec:e912} the emission rate can be written as
\begin{equation}
\dot
n_\mathrm{ion,4}\left(z\right)=-\frac{4^{\alpha_\nu}}{h\alpha_\nu}\left(1+z\right)^3\epsilon_{912}\left(z\right)\quad,
\end{equation}
with the quasar spectral index $\alpha_\nu=-1.7$ and the comoving 912\,\AA\ emissivity
$\epsilon_{912}\left(z\right)$ given by Equations~\eqref{eqn:e912_18} and \eqref{eqn:e912_21}
for $M_{1450}<-18$ and $M_{1450}<-21$, respectively.
The recombination time scale in Equation~\eqref{eqn:qHedot} is given by
\begin{equation}
  \langle t_{\rm rec}\rangle=[(1+2\chi) \langle n_\mathrm{H}\rangle \alpha_\mathrm{B}\,C]^{-1}\quad,
  \label{eq:trec}
\end{equation}
where $\langle n_\mathrm{H}\rangle=1.881\times
10^{-7}(1+z)^3$~cm$^{-3}$ is the average proper hydrogen number
density, $\alpha_\mathrm{B}$ is the Case~B \ion{He}{iii} recombination
coefficient \citep{1997MNRAS.292...27H}, and $\chi=0.079$ is the
cosmic number fraction of helium for a cosmic helium mass fraction of
$Y_\mathrm{He}=0.24$.  We assume that the clumping factor $C$ for
helium is the same as for hydrogen, for which
\citet{2012ApJ...747..100S} obtained
\begin{equation}
  C = 2.9\left(\frac{1+z}{6}\right)^{-1.1}
\end{equation}
over the redshift range $5<z<9$.

@@

Figure~\ref{fig:qhe} also shows previous solutions of
Equation~\eqref{eqn:qHedot} with different parameterizations of the
quasar emissivity, spectral energy distribution and clumping factor
\citep{2012ApJ...746..125H, 2015ApJ...813L...8M, 2016ApJ...828...90L,
  2018arXiv180104931P}, as well as the results from cosmological
radiative transfer simulations of \ion{He}{ii} reionization
\citep{2009ApJ...694..842M,2014MNRAS.445.4186C}.  The differences of
our results to the ones by \citet{2012ApJ...746..125H} and
\citet{2015ApJ...813L...8M} mostly result from differences in the
adopted quasar emissivity (Figure~\ref{fig:e912_2}).  The large quasar
emissivity adopted by \citet{2015ApJ...813L...8M} results in an early
completion of \ion{He}{ii} reionization at $z\approx 4$, which is
inconsistent with the measured strong \ion{He}{ii} absorption at
$2.7<z<3$ \citep{2016ApJ...825..144W, 2018MNRAS.473.1416M,
  2018arXiv180104931P} if the \ion{He}{ii}-ionizing background is not
fluctuating on large scales due to rare clustered and/or short-lived
quasars that result in a spatially varying mean free path of
\ion{He}{ii}-ionizing photons \citep{2010ApJ...714..355F,
  2014MNRAS.440.2406M, 2014MNRAS.437.1141D, 2017MNRAS.465.2886D}.  The
quasar emissivity considered by \citet{2012ApJ...746..125H} falls
below our determinations at the relevant redshifts
(Figure~\ref{fig:e912_2}), which results in a delayed completion of
\ion{He}{ii} reionization at $z\simeq 2.8$.

@@

In Figure~\ref{fig:qhe} we also plot $Q_\ion{He}{iii}\left(z\right)$
from two numerical simulations of quasar-driven \ion{He}{ii}
reionization \citep{2009ApJ...694..842M,2014MNRAS.445.4186C} that
broadly reproduce the measured \ion{He}{ii} effective optical depths
\citep{2016ApJ...825..144W}.  In these simulations the outputs of
$N$-body or hydrodynamic simulations are post-processed with radiative
transfer around quasars sourced according to a specific model, and the
effects of \ion{He}{ii} Lyman limit systems are approximately captured
with sub-grid filtering methods \citep{2009ApJ...694..842M} or with
adaptive mesh refinement \citep{2014MNRAS.445.4186C}.  Their different
timing of \ion{He}{ii} reionization is mostly due to the adopted
quasar model (QLF, spectral energy distribution, quasar lifetime,
anisotropic emission, halo mass range) and stochasticity in the $z\ga
3.5$ quasar number density in the limited simulation volumes.  Thus,
while current simulations do not reproduce the measured scatter in the
\ion{He}{ii} effective optical depths at $2.7<z<3.5$ in detail
\citep{2016ApJ...825..144W}, this may reflect limitations of the
modelling other than the QLF \citep{2017MNRAS.468.4691D}.  Our
$Q_\ion{He}{iii}\left(z\right)$ for $M_{1450}<-18$ agrees well with
the simulation by \citet{2014MNRAS.445.4186C}, in which \ion{He}{ii}
reionization is accomplished by the $z<5$ quasar population evolved
assuming pure density or pure luminosity evolution to match the QLF by
\citet{2011ApJ...728L..26G} for $M_{1450}<-19.5$ \citep[see
  also][]{2013MNRAS.435.3169C}.  Future efforts in numerical modelling
of \ion{He}{ii} reionization should investigate quasar models which
follow the QLF evolution in detail, and which are consistent with the
measured redshift evolution and scatter of the \ion{He}{ii} effective
optical depth, as well as the measured redshift evolution of the IGM
temperature-density relation \citep[e.g.][]{2011MNRAS.410.1096B,
  2014MNRAS.441.1916B, 2018MNRAS.474.2871R, 2017arXiv171000700H}.
